Stabilization-Free Virtual Element Methods

### 2023-01-19 stabfreevem_sinum.tex
typo
add referee's reports

% Optional PDF information
\ifpdf
\hypersetup{
  pdftitle={Robust Mixed Methods for Quad-Curl Perturbation Problem},
  pdfauthor={X. Huang and C. Zhang}
}
\fi

@@

% REQUIRED
\begin{keywords}
virtual element, stabilization-Free, macro finite element, norm equivalence, error analysis
\end{keywords}

>>>>

% Optional PDF information
\ifpdf
\hypersetup{
  pdftitle={Stabilization-Free Virtual Element Methods},
  pdfauthor={C. Chen, X. Huang and H. Wei}
}
\fi

@@

% REQUIRED
\begin{keywords}
virtual element, stabilization-free, macro finite element, norm equivalence, error analysis
\end{keywords}
